\iffalse
                       
                        
                        
                        
                    
                        \author{AI24BTECH11006 - Bugada Roopansha}
                        \section{PH}
                        \chapter{2010}
                        \fi
 


    \item If the permittivity $ \varepsilon $ and permeability $ \mu $ assume negative values in a certain frequency range, then the directions of the propagation vector $ \vec{k} $ and the Poynting vector $ \vec{S} $ in that frequency range are related as:

    \begin{enumerate}
        \item $ \vec{k} $ and $ \vec{S} $ are parallel.
        \item $ \vec{k} $ and $ \vec{S} $ are anti-parallel.
        \item $ \vec{k} $ and $ \vec{S} $ are perpendicular to each other.
        \item $ \vec{k} $ and $ \vec{S} $ make an angle that depends on the magnitudes of $ \brak{\varepsilon} $ and $ \brak{\mu} $.
    \end{enumerate}
   \section{Statments for Linked Questions $54,55$}     
     The Lagrangian for a simple pendulum is given by:
    \[
    L = \frac{1}{2} m l^2 \dot{\theta}^2 - mg l \brak{1 - \cos \theta}
    \]
    
   \item  Hamilton's equations are then given by:
    \begin{enumerate}
        \item $ \dot{p}_\theta = -mg l \sin \theta $; $ \dot{\theta} = \frac{p_\theta}{m l^2} $
        \item $ \dot{p}_\theta = -mg l \sin \theta $; $\dot{\theta} = \frac{p_\theta}{m l^2} $
        \item $ \dot{p}_\theta = -m \dot{\theta} $; $ \dot{\theta} = \frac{p_\theta}{m } $
        \item $ \dot{p_\theta}=-\brak{\frac{g}{l}} \theta $; $ \dot{\theta} = \frac{p_\theta}{m l} $
    \end{enumerate}

 
    \item The Poisson bracket between $ \theta $ and $ \dot{\theta} $ is:

    \begin{enumerate}
        \item $\brak{\theta, \dot{\theta}} = 1$
        \item $\brak{\theta, \dot{\theta}} = \frac{1}{m l^2}$
         \item $\brak{\theta, \dot{\theta}} = \frac{1}{m}$
        \item $\brak{\theta, \dot{\theta}} = \frac{g}{l}$
    \end{enumerate}

   
\section{General Aptitude (GA) Questions}

\subsection{Q.56 - Q.60 carry one mark each}


    \item Choose the most appropriate word from the options given below to complete the following sentence:

   \textbf{ His rather casual remarks on politics \dots his lack of seriousness about the subject.}

    \begin{enumerate}
        \item masked
        \item belied
        \item betrayed
        \item suppressed
    \end{enumerate}

    \item Which of the following options is the closest in meaning to the word below: 

    \textbf{Circuitous}

    \begin{enumerate}
        \item cyclic
        \item indirect
        \item confusing
        \item crooked
    \end{enumerate}

    \item Choose the most appropriate word from the options given below to complete the following sentence:

   \textbf{ If we manage to \dots  our natural resources, we would leave a better planet for our children.}

    \begin{enumerate}
        \item uphold
        \item restrain
        \item cherish
        \item conserve
    \end{enumerate}

    \item $25$ persons are in a room. $15$ of them play hockey, $17$ of them play football, and $10$ of them play both hockey and football. Then the number of persons playing neither hockey nor football is:

    \begin{enumerate}
        \item $2$
        \item $17$
        \item $13$
        \item $3$
    \end{enumerate}

    \item The question below consists of a pair of related words followed by four pairs of words. Select the pair that best expresses the relation in the original pair.

    \textbf{Unemployed: Worker}

    \begin{enumerate}
        \item fallow : land
        \item unaware : sleeper
        \item wit : jester
        \item renovated : house
    \end{enumerate}


    \subsection{ Q.61 - Q.65 carry two marks each.}


\item  If $137 + 276 = 435$, how much is $731 + 672$?

    \begin{enumerate}
        \item $534$
        \item $1403$
        \item $1623$
        \item $1513$
    \end{enumerate}





    \item Hari \brak{H}, Gita \brak{G}, Irfan \brak{I}, and Saira \brak{S} are siblings \brak{i.e., brothers and sisters}. All were born on $1$st January. The age difference between any two successive siblings \brak{that is, born one after another} is less than $3$ years. Given the following facts:
    
    \begin{itemize}
        \item Hari's age + Gita's age $\textgreater$ Irfan's age + Saira's age.
        \item There are no twins.
        \item The age difference between Gita and Saira is $1   $ year. However, Gita is not the oldest, and Saira is not the youngest.
    \end{itemize}

    In what order were they born \brak{oldest first}?

    \begin{enumerate}
        \item HSIG
        \item SGHI
        \item IGSH
        \item IHSG
    \end{enumerate}

    \item \textbf{Modern warfare has changed from large-scale clashes of armies to the suppression of civilian populations. Chemical agents that do their work silently appear to be suited to such warfare; and regretfully, there exist people in military establishments who think that chemical agents are useful tools for their cause.}

    Which of the following statements best sums up the meaning of the above passage:

    \begin{enumerate}
        \item Modern warfare has resulted in civil strife.
        \item Chemical agents are useful in modern warfare.
        \item Use of chemical agents in warfare would be undesirable.
        \item People in military establishments like to use chemical agents in war.
    \end{enumerate}

    \item $5$ skilled workers can build a wall in $20$ days; $8$ semi-skilled workers can build a wall in $25$ days; $10$ unskilled workers can build a wall in $30$ days. If a team has $2$ skilled, $6$ semi-skilled, and $5$ unskilled workers, how long will it take to build the wall?

    \begin{enumerate}
        \item $20$ days
        \item $18$ days
        \item $16$ days
        \item $15$ days
    \end{enumerate}

    \item Given the digits $2, 2, 3, 3, 3, 4, 4, 4, 4$ how many distinct $4$-digit numbers greater than $3000$ can be formed?

    \begin{enumerate}
        \item $50$
        \item $51$
        \item $52$
        \item $54$
    \end{enumerate}




    



