\iffalse
                       
                        
                        
                        
                    
\author{AI24BTECH11006 - Bugada Roopansha}
\section{ME}
\chapter{2009}
\fi
                            
 \item What are the upper and lower limits of the shaft represented by $60 \, f_8$?
    
    Use the following data:
    \begin{itemize}
        \item Diameter $60$ lies in the diameter step of $50 - 80$ mm.
        \item Fundamental tolerance unit, $i$, in $\mu$m = $0.45 \brak{D^{1/3}} + 0.001 D$, where $D$ is the representative size in mm.
        \item Tolerance value for $IT8 = 25i$.
        \item Fundamental deviation for `$f$` shaft $= -5.5 D^{0.41}$.
    \end{itemize}
    
    \begin{enumerate}
        \item Lower limit $= 59.924$ mm, Upper limit $= 59.970$ mm
        \item Lower limit $= 59.954$ mm, Upper limit $= 60.000$ mm
        \item Lower limit $= 59.970$ mm, Upper limit $= 60.016$ mm
        \item Lower limit $= 60.000$ mm, Upper limit $= 60.046$ mm
    \end{enumerate}
    
    \item Match the items in Column I and Column II.
    
    \input{tables/table1.tex}
    
    \begin{enumerate}
        \item $P - 1, Q - 3, R - 2, S - 4$
        \item $P - 1, Q - 4, R - 2, S - 3$
        \item $P - 3, Q - 4, R - 2, S - 1$
        \item $P - 4, Q - 1, R - 2, S - 3$
    \end{enumerate}
  

  \section{  Common Data for Questions 51 and 52:}
    
    The inlet and outlet conditions of steam for an adiabatic steam turbine are as indicated in the figure. The notations are as usually followed.
    
    \begin{itemize}
        \item $h_1 = 3200 \, \frac{kJ}{kg}$
        \item $V_1 = 160 \, \frac{m}{s}$
        \item $Z_1 = 10 \, m$
        \item $P_1 = 3 \, MPa$
        \item $h_2 = 2600 \, \frac{kJ}{kg}$
        \item $V_2 = 100 \, \frac{m}{s}$
        \item $Z_2 = 6 \, m$
        \item $P_2 = 70 \, kPa$
    \end{itemize}

    \item If mass flow rate of steam through the turbine is $20 \, \frac{kg}{s}$, the power output of the turbine $\brak{in 
 MW}$ is
    \begin{enumerate}
        \item $12.157$
        \item $12.941$
        \item $168.001$
        \item $168.785$
    \end{enumerate}

    \item Assume the above turbine to be part of a simple Rankine cycle. The density of water at the inlet to the pump is $1000 \, \frac{kg}{m^3}$. Ignoring kinetic and potential energy effects, the specific work $\brak{in \frac{kJ}{kg}}$ supplied to the pump is
    \begin{enumerate}
        \item $0.293$
        \item $0.351$
        \item $2.930$
        \item $3.510$
    \end{enumerate}

   \section{ Common Data for Questions 53 and 54:}
    
    Radiative heat transfer is intended between the inner surfaces of two very large isothermal parallel metal plates. While the upper plate $\brak{designated as plate 1}$ is a black surface and is the warmer one being maintained at $727 $\degree C, the lower plate \brak{plate 2} is a diffuse and gray surface with an emissivity of $0.7$ and is kept at $227 $\degree C. Assume that the surfaces are sufficiently large to form a two-surface enclosure and steady-state conditions to exist. Stefan-Boltzmann constant is given as $5.67 \times 10^{-8} \, \frac{W}{{m}^2{K}^4}$.

\item The irradiation \brak{in \frac{\text{kW}}{\text{m}^2}} for the upper plate \brak{plate 1} is


    \begin{enumerate}
        \item $2.5$
        \item $3.6$
        \item $17.0$
        \item $19.5$
    \end{enumerate}

    \item If plate $1$ is also a diffuse and gray surface with an emissivity value of $0.8$, the net radiation heat exchange \brak{in \frac{\text{kW}}{\text{m}^2}} between plate $1$ and plate $2$ is
    \begin{enumerate}
        \item $17.0$
        \item $19.5$
        \item $23.0$
        \item $31.7$
    \end{enumerate} 

\section{ Common Data for Questions 55 and 56:}
    
    Consider the following PERT network:
    
   \input{figs/fig1.tex}

    The optimistic time, most likely time, and pessimistic time of all the activities are given in the table below:
    
    \input{tables/table2.tex}
    \item The critical path duration of the network \brak{in days} is
    \begin{enumerate}
        \item $11$
        \item $14$
        \item $17$
        \item $18$
    \end{enumerate}

    \item The standard deviation of the critical path is
    \begin{enumerate}
        \item $0.33$
        \item $0.55$
        \item $0.77$
        \item $1.66$
    \end{enumerate}

    

   \section{ Statement for Linked Answer Questions 57 and 58:}
    
    In a machining experiment, tool life was found to vary with the cutting speed in the following manner:
    
    \input{tables/table3.tex}
    \item The exponent $\brak{n}$ and constant $\brak{k}$ of the Taylor's tool life equation are
    \begin{enumerate}
        \item $n = 0.5$ and $k = 540$
        \item $n = 1$ and $k = 4860$
        \item $n = -1$ and $k = 0.74$
        \item $n = -0.5$ and $k = 1.155$
    \end{enumerate}
    \item  What is the percentage increase in tool life when the cutting speed is halved?
    \begin{enumerate}
        \item $50\%$
        \item $200\%$
        \item $300\%$
        \item $400\%$
    \end{enumerate}

\section{ Statement for Linked Answer Questions 59 and 60}
    
  \item   A $20$\degree full depth involute spur pinion of $4$ mm module and $21$ teeth is to transmit $15$ kW at $960$ rpm. Its face width is $25$ mm.

    \item  The tangential force transmitted \brak{in N} is
    \begin{enumerate}
        \item $3552$
        \item $2611$
        \item $1776$
        \item $1305$
    \end{enumerate}

    \item  Given that the tooth geometry factor is $0.32$ and the combined effect of dynamic load and allied factors intensifying the stress is $1.5$; the minimum allowable stress \brak{in MPa} for the gear material is
    \begin{enumerate}
        \item $242.0$
        \item $166.5$
        \item $121.0$
        \item $74.0$
    \end{enumerate}

